A sensor grid approach for large scale acoustic monitoring

### 2017-06-16 paper/article.tex
new comments

\title{An effective sensor grid approach for large scale acoustic monitoring}

@@

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\columnwidth]{class_mel_q.eps}
	\caption{Classification accuracy as a function of word size before encoding. The baseline on the right is computed without quantizing the representation.}
	\label{fig:class_mel_q}
\end{figure}

@@

\begin{table*}[h]
\centering
\caption{Classification accuracy for varying representation resolutions}
\label{T1}
\begin{tabular}{ll|c|c|c|c|c|c|c|}
\cline{3-9}
\multicolumn{2}{c}{\multirow{2}{*}{SVM}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
 & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9}
\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
 & \multicolumn{1}{|c|}{10} & 0.55$\pm$0.03 & 0.60$\pm$0.03 & \textbf{0.61$\pm$0.04} & \textbf{0.62$\pm$0.03} & \textbf{0.62$\pm$0.04} & \textbf{0.63$\pm$0.06} & \textbf{0.65$\pm$0.06} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{20} & \textbf{0.58$\pm$0.04} & \textbf{0.62$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.65$\pm$0.05} & \textbf{0.67$\pm$0.06} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{30} & \textbf{\textcolor{red}{0.60$\pm$0.03}} & \textbf{\textcolor{red}{0.64$\pm$0.04}} & \textbf{\textcolor{red}{0.64$\pm$0.04}} & \textbf{\textcolor{red}{0.65$\pm$0.04}} & \textbf{\textcolor{red}{0.65$\pm$0.03}} & \textbf{\textcolor{red}{0.67$\pm$0.04}} & \textbf{\textcolor{red}{0.68$\pm$0.04}} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{40} & \textbf{0.60$\pm$0.03} & \textbf{0.63$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.66$\pm$0.04} & \textbf{0.68$\pm$0.05} \\ \cline{1-9}
\end{tabular}

@@

Finally, objective intelligibility metrics are estimated for the studied parameters and compared to an informal perceptual evaluation \footnote{Decoded speech utterances for various conditions can be listened to at \url{http://}}. Figure~\ref{fig:int_mel_avg} shows both the CSII and fwSNRseg indicators for varying representation dimensions. Figure~\ref{fig:percint_mel_avg} presents the results of the preliminar perceptual test \ml{comment tu as fait le test ?} for the same setup. We acknowledge that it is surely biased by a reduced number of participants and lack of tested audio material. However, it is sufficient to judge the relevance of objective indicators in our conditions as we can observe a correlation between the three metrics.

>>>>

\title{A sensor grid approach for large scale acoustic monitoring}

@@

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\columnwidth]{class_mel_q.eps}
	\caption{Classification accuracy as a function of word size before encoding. The baseline on the right is computed without quantizing the representation. \ml{cette figure pose probleme, car la baseline n'a pas de word size, je mettrai un tick "no quant". Pourquoi les lignes continues jqa la baseline ?}}
	\label{fig:class_mel_q}
\end{figure}

@@

\begin{table*}[h]
	\ml{percentage}
\centering
\caption{Classification accuracy for varying representation resolutions}
\label{T1}
\begin{tabular}{ll|c|c|c|c|c|c|c|}
\cline{3-9}
\multicolumn{2}{c}{\multirow{2}{*}{SVM}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
 & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9}
\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
 & \multicolumn{1}{|c|}{10} & 0.55$\pm$0.03 & 0.60$\pm$0.03 & \textbf{0.61$\pm$0.04} & \textbf{0.62$\pm$0.03} & \textbf{0.62$\pm$0.04} & \textbf{0.63$\pm$0.06} & \textbf{0.65$\pm$0.06} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{20} & \textbf{0.58$\pm$0.04} & \textbf{0.62$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.65$\pm$0.05} & \textbf{0.67$\pm$0.06} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{30} & \textbf{\textcolor{red}{0.60$\pm$0.03}} & \textbf{\textcolor{red}{0.64$\pm$0.04}} & \textbf{\textcolor{red}{0.64$\pm$0.04}} & \textbf{\textcolor{red}{0.65$\pm$0.04}} & \textbf{\textcolor{red}{0.65$\pm$0.03}} & \textbf{\textcolor{red}{0.67$\pm$0.04}} & \textbf{\textcolor{red}{0.68$\pm$0.04}} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{40} & \textbf{0.60$\pm$0.03} & \textbf{0.63$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.66$\pm$0.04} & \textbf{0.68$\pm$0.05} \\ \cline{1-9}
\end{tabular}

@@

Finally, objective intelligibility metrics are estimated for the studied parameters and compared to an informal perceptual evaluation \footnote{Decoded speech utterances for various conditions can be listened to at \url{http://}}. Figure~\ref{fig:int_mel_avg} shows both the CSII and fwSNRseg indicators for varying representation dimensions. Figure~\ref{fig:percint_mel_avg} presents the results of the preliminar perceptual test \ml{soit on fait un test avec 5-10 personnes soit on en parle pas} for the same setup. We acknowledge that it is surely biased by a reduced number of participants and lack of tested audio material. However, it is sufficient to judge the relevance of objective indicators in our conditions as we can observe a correlation between the three metrics.
